---
title: "maaDDM2phi"
author: "Jennifer March (jennifer.march@uni-hamburg.de)"
date: "3/26/2024"
output: html_document
---

# General Info

This script contains all the models tested in our manuscript (https://osf.io/preprints/psyarxiv/wvfnb). It requires JAGS. The script is structured s follows:

1. **Preparation:** loading libraries and load workspace
2. **Multi-attribute attentional DDM with 2Phi:** Function, Estimate maaDDM2phi, Test Parameters and some graphs (corresponds to maaDDM2phi)

# 1 Preparations
## 1.1 Load Libraries
```{r}
#clear working environment
rm(list=ls())

#clear all plots
#if(!is.null(dev.list())) dev.off()

#load required libraries
library(rtdists)
library(dfoptim)
library(readxl)
library(tidyr)
library(dplyr)
library(zoo)
library(tibble)
library(readr)
pacman::p_load(tidyverse, ez)
#parallel computing stuff
library(parallel)
library(doParallel)
library(foreach)
numCores <- detectCores()
registerDoParallel(cores=numCores)
#JAGS packages
library(R2jags) #should be put at the start but keep it here for the moment...
library(rtdists) #to be on the safe side when loading workspace (and not executing the first chunk above)
```

## 1.2 Load workspace 
```{r}
# Load data for taste
load("data_prep.RData")

```


# 2 maaDDM_2Phi
## 2.1 Estimate maaDDM_2Phi with hierarchical Bayesian modeling (JAGS)

```{r}
# get data and initial values together and specify the model
#a) Wanting vs health
ddmData <- list('N'=N,'S'=S,'P'=P,'H'=H,'tasteA'=prefA,'tasteB'=prefB,'healthA'=healthA,'healthB'=healthB,'RT'=RT,
                'fixProp1'=fixProp1,'fixProp2'=fixProp2,'fixProp3'=fixProp3,'fixProp4'=fixProp4)

# #b) Wanting vs nutri
# ddmData <- list('N'=N,'S'=S,'P'=P,'H'=H,'tasteA'=prefA,'tasteB'=prefB,'healthA'=nutriA,'healthB'=nutriB,'RT'=RT,
#                 'fixProp1'=fixProp1,'fixProp2'=fixProp2,'fixProp3'=fixProp3,'fixProp4'=fixProp4)


#starting values
nChains <- 8

#parallel computing apparently not possible
T1<-Sys.time()
addmJAGS_2Phi_want <- jags.parallel(ddmData,inits = NULL,#jags.seed = sample(100:999,1),
                    parameters.to.save = c('mu_bound','sigma_bound','mu_ndt','sigma_ndt',
                                           'mu_drift','sigma_drift','mu_weight1','sigma_weight1',
                                           'mu_theta','sigma_theta','mu_phy','sigma_phy','mu_phy2','sigma_phy2',
                                           'mu_bound_H','sigma_bound_H','mu_ndt_H','sigma_ndt_H',
                                           'mu_drift_H','sigma_drift_H','mu_weight1_H','sigma_weight1_H',
                                           'mu_theta_H','sigma_theta_H','mu_phy_H','sigma_phy_H','mu_phy2_H','sigma_phy2_H',
                                           'bound','ndt','drift','weight1','theta','phy','phy2',
                                           'bound_H','ndt_H','drift_H','weight1_H','theta_H','phy_H','phy2_H'),
                    model.file = "BayesModel_maaDDM_2Phi.txt",working.directory = 'BayesModels',
                    n.chains = nChains, n.iter = 60000, n.burnin = 30000,n.thin = 12, DIC = TRUE,jags.module = c("glm","dic","wiener"))
T2<-Sys.time() #T2-T1

# check convergence
ddmRhats <- addmJAGS_2Phi_want$BUGSoutput$summary[,8] #check with max(Rhats), which should ideally be < 1.01 (1.05 would also be okay)
max(ddmRhats)
addmJAGS_2Phi_want$BUGSoutput$DIC
#max R_hat = 1.053; DIC = 65134

save.image("Fit_amaDDM_want.RData")
```

## 2.2 maaDDM_2Phi: check parameters (group posteriors)
```{r}
boundSep_S <- log(1+exp(addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_bound))
boundSep_H <- log(1+exp(addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_bound+addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_bound_H))
boundSep_delta <- addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_bound_H

ndt_S <- log(1+exp(addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_ndt))
ndt_H <- log(1+exp(addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_ndt+addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_ndt_H))
ndt_delta <- addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_ndt_H

drift_S <- log(1+exp(addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_drift))
drift_H <- log(1+exp(addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_drift+addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_drift_H))
drift_delta <- addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_drift_H

weight1_S <- pnorm(addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_weight1)
weight1_H <- pnorm(addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_weight1+addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_weight1_H)
weight1_delta <- addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_weight1_H

theta_S <- (addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_theta)
theta_H <- (addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_theta+addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_theta_H)
theta_delta <- addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_theta_H

phy_S <- (addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_phy)
phy_H <- (addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_phy+addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_phy_H)
phy_delta <- addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_phy_H

phy2_S <- (addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_phy2)
phy2_H <- (addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_phy2+addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_phy2_H)
phy2_delta <- addmJAGS_2Phi_want$BUGSoutput$sims.list$mu_phy2_H


# PLOT 

#1) Weight 
histGran <- (-300:300)/150
# Create a data frame
datatw <- data.frame(weight1_S = weight1_S, weight1_H = weight1_H)
# Plot using ggplot2
tasteweight1<-ggplot(datatw, aes(x = weight1_S)) +
  geom_histogram(binwidth = 1/90, fill = "cornflowerblue", alpha = 0.5, color = "black") +
  geom_histogram(aes(x = weight1_H), binwidth = 1/100, fill = "gold", alpha = 0.5, color = "black") +
  labs(x = "Want Weight", y = "Frequency") +
  #scale_x_continuous(limits = c(-0.1, 0.25)) +
  ylim(0, 5000)+
  myTheme
# effect of hunger 
data_deltatw <- data.frame(weight1_delta = weight1_delta)
HDI_tw <- quantile(weight1_delta,c(.025,.975))
# Plot using ggplot2
tasteweight2<-ggplot(data_deltatw, aes(x = weight1_delta)) +
  geom_histogram(binwidth = 1/20, fill = "grey", alpha = 0.5, color = "black") +
  geom_vline(xintercept = 0, color = "red", size = 1.5) +
  geom_vline(xintercept = HDI_tw, color = "black", size = 1, linetype = "dashed") +
  ylim(0, 5000)+
  labs(x = "Effect of Hunger", y = "Frequency") +
  myTheme

HDI_ws <- quantile(weight1_S,c(.025,.975))
HDI_wh <- quantile(weight1_H,c(.025,.975))

# 2) Scaling
histGran <- (-300:300)/150
# Create a data frame
datascale <- data.frame(drift_S = drift_S, drift_H = drift_H)
# Plot using ggplot2
drift1<-ggplot(datascale, aes(x = drift_S)) +
  geom_histogram(binwidth = 1/150, fill = "cornflowerblue", alpha = 0.5, color = "black") +
  geom_histogram(aes(x = drift_H), binwidth = 1/150, fill = "gold", alpha = 0.5, color = "black") +
  labs(x = "Drift Scaling", y = "Frequency") +
  ylim(0, 5000)+
  #scale_x_continuous(limits = c(-0.1, 0.25)) +
  myTheme

# effect of hunger 
data_deltascale <- data.frame(drift_delta = drift_delta)
HDI_drift <- quantile(drift_delta,c(.025,.975))
# Plot using ggplot2
drift2<-ggplot(data_deltascale, aes(x = drift_delta)) +
  geom_histogram(binwidth = 1/40, fill = "grey", alpha = 0.5, color = "black") +
  geom_vline(xintercept = 0, color = "red", size = 1.5) +
  geom_vline(xintercept = HDI_drift, color = "black", size = 1, linetype = "dashed") +
  ylim(0, 5000)+
  labs(x = "Effect of Hunger", y = "Frequency") +
  myTheme

#3) Boundary seperation
histGran <- (-300:300)/150
# Create a data frame
databound <- data.frame(boundSep_S = boundSep_S, boundSep_H = boundSep_H)
# Plot using ggplot2
bound1<-ggplot(databound, aes(x = boundSep_S)) +
  geom_histogram(binwidth = 1/30, fill = "cornflowerblue", alpha = 0.5, color = "black") +
  geom_histogram(aes(x = boundSep_H), binwidth = 1/30, fill = "gold", alpha = 0.5, color = "black") +
  labs(x = "Boundary Seperation", y = "Frequency") +
  #scale_x_continuous(limits = c(-0.1, 0.25)) +
  ylim(0, 5000)+
  myTheme
# effect of hunger 
data_deltabound <- data.frame(boundSep_delta = boundSep_delta)
HDI_bound <- quantile(boundSep_delta,c(.025,.975))
# Plot using ggplot2
bound2<-ggplot(data_deltabound, aes(x = boundSep_delta)) +
  geom_histogram(binwidth = 1/40, fill = "grey", alpha = 0.5, color = "black") +
  geom_vline(xintercept = 0, color = "red", size = 1.5) +
  geom_vline(xintercept = HDI_bound, color = "black", size = 1, linetype = "dashed") +
  ylim(0, 5000)+
  labs(x = "Effect of Hunger", y = "Frequency") +
  myTheme

# 4) nDT
histGran <- (-300:300)/150
# Create a data frame
datanDT <- data.frame(ndt_S = ndt_S, ndt_H = ndt_H)
# Plot using ggplot2
nDT1<-ggplot(datanDT, aes(x = ndt_S)) +
  geom_histogram(binwidth = 1/140, fill = "cornflowerblue", alpha = 0.5, color = "black") +
  geom_histogram(aes(x = ndt_H), binwidth = 1/140, fill = "gold", alpha = 0.5, color = "black") +
  labs(x = "Non-Decision Time", y = "Frequency") +
  ylim(0, 5000)+
  #scale_x_continuous(limits = c(-0.1, 0.25)) +
  myTheme

# effect of hunger 
data_deltandt <- data.frame(ndt_delta = ndt_delta)
HDI_ndt <- quantile(ndt_delta,c(.025,.975))
# Plot using ggplot2
nDT2<-ggplot(data_deltandt, aes(x = ndt_delta)) +
  geom_histogram(binwidth = 1/110, fill = "grey", alpha = 0.5, color = "black") +
  geom_vline(xintercept = 0, color = "red", size = 1.5) +
  geom_vline(xintercept = HDI_ndt, color = "black", size = 1, linetype = "dashed") +
  ylim(0, 5000)+
  labs(x = "Effect of Hunger", y = "Frequency") +
  myTheme


# 5) Theta
histGran <- (-300:300)/150
# Create a data frame
datatheta <- data.frame(theta_S = theta_S, theta_H = theta_H)
# Plot using ggplot2
theta1<-ggplot(datatheta, aes(x = theta_S)) +
  geom_histogram(binwidth = 1/70, fill = "cornflowerblue", alpha = 0.5, color = "black") +
  geom_histogram(aes(x = theta_H), binwidth = 1/70, fill = "gold", alpha = 0.5, color = "black") +
  labs(x = "Theta", y = "Frequency") +
  ylim(0, 5000)+
  #scale_x_continuous(limits = c(-0.1, 0.25)) +
  myTheme

# effect of hunger 
data_deltatheta <- data.frame(theta_delta = theta_delta)
HDI_theta <- quantile(theta_delta,c(.025,.975))
# Plot using ggplot2
theta2<-ggplot(data_deltatheta, aes(x = theta_delta)) +
  geom_histogram(binwidth = 1/70, fill = "grey", alpha = 0.5, color = "black") +
  geom_vline(xintercept = 0, color = "red", size = 1.5) +
  geom_vline(xintercept = HDI_theta, color = "black", size = 1, linetype = "dashed") +
  ylim(0, 5000)+
  labs(x = "Effect of Hunger", y = "Frequency") +
  myTheme


# 6) Phi 1 (taste)
histGran <- (-300:300)/150
# Create a data frame
dataphy <- data.frame(phy_S = phy_S, phy_H = phy_H)
# Plot using ggplot2
phy1<-ggplot(dataphy, aes(x = phy_S)) +
  geom_histogram(binwidth = 1/25, fill = "cornflowerblue", alpha = 0.5, color = "black") +
  geom_histogram(aes(x = phy_H), binwidth = 1/25, fill = "gold", alpha = 0.5, color = "black") +
  labs(x = "Phi Taste", y = "Frequency") +
  ylim(0, 5000)+
  #scale_x_continuous(limits = c(-0.1, 0.25)) +
  myTheme

# effect of hunger 
data_deltaphy <- data.frame(phy_delta = phy_delta)
HDI_phy <- quantile(phy_delta,c(.025,.975))
# Plot using ggplot2
phy2<-ggplot(data_deltaphy, aes(x = phy_delta)) +
  geom_histogram(binwidth = 1/25, fill = "grey", alpha = 0.5, color = "black") +
  geom_vline(xintercept = 0, color = "red", size = 1.5) +
  geom_vline(xintercept = HDI_phy, color = "black", size = 1, linetype = "dashed") +
  ylim(0, 5000)+
  labs(x = "Effect of Hunger", y = "Frequency") +
  myTheme

# 7) Phi2 (health)
histGran <- (-300:300)/150
# Create a data frame
dataphy2 <- data.frame(phy2_S = phy2_S, phy2_H = phy2_H)
# Plot using ggplot2
phy3<-ggplot(dataphy2, aes(x = phy2_S)) +
  geom_histogram(binwidth = 1/15, fill = "cornflowerblue", alpha = 0.5, color = "black") +
  geom_histogram(aes(x = phy2_H), binwidth = 1/15, fill = "gold", alpha = 0.5, color = "black") +
  labs(x = "Phi Health", y = "Frequency") +
  ylim(0, 5000)+
  #scale_x_continuous(limits = c(-0.1, 0.25)) +
  myTheme

# effect of hunger 
data_deltaphy2 <- data.frame(phy2_delta = phy2_delta)
HDI_phy2 <- quantile(phy2_delta,c(.025,.975))
# Plot using ggplot2
phy4<-ggplot(data_deltaphy2, aes(x = phy2_delta)) +
  geom_histogram(binwidth = 1/10, fill = "grey", alpha = 0.5, color = "black") +
  geom_vline(xintercept = 0, color = "red", size = 1.5) +
  geom_vline(xintercept = HDI_phy2, color = "black", size = 1, linetype = "dashed") +
  ylim(0, 5000)+
  labs(x = "Effect of Hunger", y = "Frequency") +
  myTheme

HDI_phis <- quantile(phy2_S,c(.025,.975))
HDI_phih <- quantile(phy2_H,c(.025,.975))


library("cowplot")
# Arrange the plots side by side
combined_plot_maaddm2phi2 <- plot_grid(tasteweight1, tasteweight2, drift1, drift2, nDT1, nDT2, bound1, bound2, theta1, theta2, phy1, phy2, phy3, phy4, labels = c("a", "", "b", "", "c", "", "d", "", "e", "", "f", "", "g", ""), label_size = 20, ncol = 4, align = "h", column_spacing = unit(c(1, 3, 1, 1, 3, 1, 1, 3, 1,1,3,1), "cm"))
combined_plot_maaddm2phi2
# Save the combined plot as a PNG file
ggsave("combined_plot_maaddm2phi_want.png", combined_plot_maaddm2phi2, width = 16, height = 12)

```
