---
title: "mtDDM"
author: "Jennifer March (jennifer.march@uni-hamburg.de)"
date: "3/26/2024"
output: html_document
---

# General Info

This script contains all the models tested in our manuscript (https://osf.io/preprints/psyarxiv/wvfnb). It requires JAGS. The script is structured s follows:

1. **Preparation:** loading libraries and load workspace
2. **Multi-attribute time-dependent DDM:** Function, Estimate mtDDM, Test Parameters and some graphs (corresponds to mtDDM)
*note* the change compared to the main taste-health analyses: We merely exchange nutri as input DDMdata (line 75) and adept the saved workspace and plot.


# 1 Preparations
## 1.1 Load Libraries
```{r}
#clear working environment
rm(list=ls())

#clear all plots
#if(!is.null(dev.list())) dev.off()

#load required libraries
library(rtdists)
library(dfoptim)
library(readxl)
library(tidyr)
library(dplyr)
library(zoo)
library(tibble)
library(readr)
pacman::p_load(tidyverse, ez)
#parallel computing stuff
library(parallel)
library(doParallel)
library(foreach)
numCores <- detectCores()
registerDoParallel(cores=numCores)
#JAGS packages
library(R2jags) #should be put at the start but keep it here for the moment...
library(rtdists) #to be on the safe side when loading workspace (and not executing the first chunk above)
```

## 1.2 Load workspace (if required)
```{r}
# Load data
load("data_prep.RData")
```

## 1.3 Chreate Theme for figures
```{r}
library(ggplot2)
myTheme <- theme(
  axis.line = element_line(colour = "black"), 
  panel.grid.major = element_blank(), 
  panel.grid.minor = element_blank(),  
  panel.border = element_blank(),   
  panel.background = element_blank(),
  text=element_text(size=16, colour = "black"), 
  axis.title.x = element_text(size=20, face="bold", colour = "black"), 
  axis.title.y = element_text( size=20, face="bold", colour = "black"),
  axis.text = element_text(size=16),
  strip.text =  element_text( size=16),
  strip.background = element_rect(fill = "white", colour = "black"),
  legend.background = element_rect(colour = "black"),
  legend.key = element_blank(),
  legend.key.size = unit(3, "lines"))
```

# 2 mtDDM
## 2.1 Estimate maDDM_rst with hierarchical Bayesian modeling (JAGS)
```{r}
# get data and initial values together and specify the model
ddmData <- list('N'=N,'S'=S,'P'=P,'H'=H,'tasteA'=tasteA,'tasteB'=tasteB,'healthA'=nutriA,'healthB'=nutriB,'RT'=RT,'RT2'=abs(RT))

#starting values
nChains <- 8

#parallel computing apparently not possible
T1<-Sys.time()
ddmJAGS_rst_nutri <- jags.parallel(ddmData,inits = NULL,#jags.seed = sample(100:999,1),
                    parameters.to.save = c('mu_bound','sigma_bound','mu_ndt','sigma_ndt',
                                           'mu_drift','sigma_drift','mu_weight1','sigma_weight1',
                                           'mu_rst','sigma_rst',
                                           'mu_bound_H','sigma_bound_H','mu_ndt_H','sigma_ndt_H',
                                           'mu_drift_H','sigma_drift_H','mu_weight1_H','sigma_weight1_H',
                                           'mu_rst_H','sigma_rst_H',
                                           'bound','ndt','drift','weight1','rst',
                                           'bound_H','ndt_H','drift_H','weight1_H','rst_H'),
                    model.file = "BayesModel_maDDM_rst.txt",working.directory = 'BayesModels',
                    n.chains = nChains, n.iter = 60000, n.burnin = 30000,n.thin = 12, DIC = TRUE,jags.module = c("glm","dic","wiener"))
T2<-Sys.time() #T2-T1

# check convergence
ddmRhats <- ddmJAGS_rst_nutri$BUGSoutput$summary[,8] #check with max(Rhats), which should ideally be < 1.01 (1.05 would also be okay)
max(ddmRhats)
ddmJAGS_rst_nutri$BUGSoutput$DIC
#Recommended to save ddmJAGS_rst_nutri
save.image(file="mtDDM_nutri.RData")

```

## 2.2 maDDM_rst: check parameters (group posteriors)
```{r}
boundSep_S <- log(1+exp(ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_bound))
boundSep_H <- log(1+exp(ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_bound+ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_bound_H))
boundSep_delta <- ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_bound_H

ndt_S <- log(1+exp(ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_ndt))
ndt_H <- log(1+exp(ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_ndt+ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_ndt_H))
ndt_delta <- ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_ndt_H

weight1_S <- pnorm(ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_weight1)
weight1_H <- pnorm(ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_weight1+ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_weight1_H)
weight1_delta <- ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_weight1_H

drift_S <- log(1+exp(ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_drift))
drift_H <- log(1+exp(ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_drift+ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_drift_H))
drift_delta <- ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_drift_H

rst_S <- ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_rst
rst_H <- ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_rst+ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_rst_H
rst_delta <- ddmJAGS_rst_nutri$BUGSoutput$sims.list$mu_rst_H

##plot each parameter

#1) Weight 
histGran <- (-300:300)/150
# Create a data frame
datatw <- data.frame(weight1_S = weight1_S, weight1_H = weight1_H)
# Plot using ggplot2
tasteweight1<-ggplot(datatw, aes(x = weight1_S)) +
  geom_histogram(binwidth = 1/230, fill = "cornflowerblue", alpha = 0.5, color = "black") +
  geom_histogram(aes(x = weight1_H), binwidth = 1/250, fill = "gold", alpha = 0.5, color = "black") +
  labs(x = "Taste Weight", y = "Frequency") +
  #scale_x_continuous(limits = c(-0.1, 0.25)) +
  ylim(0, 5000)+
  myTheme
# effect of hunger 
data_deltatw <- data.frame(weight1_delta = weight1_delta)
HDI_tw <- quantile(weight1_delta,c(.025,.975))
# Plot using ggplot2
tasteweight2<-ggplot(data_deltatw, aes(x = weight1_delta)) +
  geom_histogram(binwidth = 1/10, fill = "grey", alpha = 0.5, color = "black") +
  geom_vline(xintercept = 0, color = "red", size = 1.5) +
  geom_vline(xintercept = HDI_tw, color = "black", size = 1, linetype = "dashed") +
  ylim(0, 5000)+
  labs(x = "Effect of Hunger", y = "Frequency") +
  myTheme

HDI_ws <- quantile(weight1_S,c(.025,.975))
HDI_wh <- quantile(weight1_H,c(.025,.975))

# 2) Scaling
histGran <- (-300:300)/150
# Create a data frame
datascale <- data.frame(drift_S = drift_S, drift_H = drift_H)
# Plot using ggplot2
drift1<-ggplot(datascale, aes(x = drift_S)) +
  geom_histogram(binwidth = 1/170, fill = "cornflowerblue", alpha = 0.5, color = "black") +
  geom_histogram(aes(x = drift_H), binwidth = 1/170, fill = "gold", alpha = 0.5, color = "black") +
  labs(x = "Drift Scaling", y = "Frequency") +
  ylim(0, 5000)+
  #scale_x_continuous(limits = c(-0.1, 0.25)) +
  myTheme

# effect of hunger 
data_deltascale <- data.frame(drift_delta = drift_delta)
HDI_drift <- quantile(drift_delta,c(.025,.975))
# Plot using ggplot2
drift2<-ggplot(data_deltascale, aes(x = drift_delta)) +
  geom_histogram(binwidth = 1/70, fill = "grey", alpha = 0.5, color = "black") +
  geom_vline(xintercept = 0, color = "red", size = 1.5) +
  geom_vline(xintercept = HDI_drift, color = "black", size = 1, linetype = "dashed") +
  ylim(0, 5000)+
  labs(x = "Effect of Hunger", y = "Frequency") +
  myTheme

# 3) RST
histGran <- (-300:300)/150
# Create a data frame
datarst <- data.frame(rst_S = rst_S, rst_H = rst_H)
# Plot using ggplot2
rst1<-ggplot(datarst, aes(x = rst_S)) +
  geom_histogram(binwidth = 1/2200, fill = "cornflowerblue", alpha = 0.5, color = "black") +
  geom_histogram(aes(x = rst_H), binwidth = 1/2200, fill = "gold", alpha = 0.5, color = "black") +
  labs(x = "Relative Starting Time", y = "Frequency") +
  ylim(0, 5000)+
  #scale_x_continuous(limits = c(-0.1, 0.25)) +
  myTheme


# effect of hunger 
data_deltarst <- data.frame(rst_delta = rst_delta)
HDI_rst <- quantile(rst_delta,c(.025,.975))
# Plot using ggplot2
rst2<-ggplot(data_deltarst, aes(x = rst_delta)) +
  geom_histogram(binwidth = 1/1300, fill = "grey", alpha = 0.5, color = "black") +
  geom_vline(xintercept = 0, color = "red", size = 1.5) +
  geom_vline(xintercept = HDI_rst, color = "black", size = 1, linetype = "dashed") +
  ylim(0, 5000)+
  labs(x = "Effect of Hunger", y = "Frequency") +
  myTheme

#4) Boundary seperation
histGran <- (-300:300)/150
# Create a data frame
databound <- data.frame(boundSep_S = boundSep_S, boundSep_H = boundSep_H)
# Plot using ggplot2
bound1<-ggplot(databound, aes(x = boundSep_S)) +
  geom_histogram(binwidth = 1/30, fill = "cornflowerblue", alpha = 0.5, color = "black") +
  geom_histogram(aes(x = boundSep_H), binwidth = 1/30, fill = "gold", alpha = 0.5, color = "black") +
  labs(x = "Boundary Seperation", y = "Frequency") +
  #scale_x_continuous(limits = c(-0.1, 0.25)) +
  ylim(0, 5000)+
  myTheme
# effect of hunger 
data_deltabound <- data.frame(boundSep_delta = boundSep_delta)
HDI_bound <- quantile(boundSep_delta,c(.025,.975))
# Plot using ggplot2
bound2<-ggplot(data_deltabound, aes(x = boundSep_delta)) +
  geom_histogram(binwidth = 1/40, fill = "grey", alpha = 0.5, color = "black") +
  geom_vline(xintercept = 0, color = "red", size = 1.5) +
  geom_vline(xintercept = HDI_bound, color = "black", size = 1, linetype = "dashed") +
  ylim(0, 5000)+
  labs(x = "Effect of Hunger", y = "Frequency") +
  myTheme

# 5) nDT
histGran <- (-300:300)/150
# Create a data frame
datanDT <- data.frame(ndt_S = ndt_S, ndt_H = ndt_H)
# Plot using ggplot2
nDT1<-ggplot(datanDT, aes(x = ndt_S)) +
  geom_histogram(binwidth = 1/140, fill = "cornflowerblue", alpha = 0.5, color = "black") +
  geom_histogram(aes(x = ndt_H), binwidth = 1/140, fill = "gold", alpha = 0.5, color = "black") +
  labs(x = "Non-Decision Time", y = "Frequency") +
  ylim(0, 5000)+
  #scale_x_continuous(limits = c(-0.1, 0.25)) +
  myTheme

# effect of hunger 
data_deltandt <- data.frame(ndt_delta = ndt_delta)
HDI_ndt <- quantile(ndt_delta,c(.025,.975))
# Plot using ggplot2
nDT2<-ggplot(data_deltandt, aes(x = ndt_delta)) +
  geom_histogram(binwidth = 1/110, fill = "grey", alpha = 0.5, color = "black") +
  geom_vline(xintercept = 0, color = "red", size = 1.5) +
  geom_vline(xintercept = HDI_ndt, color = "black", size = 1, linetype = "dashed") +
  ylim(0, 5000)+
  labs(x = "Effect of Hunger", y = "Frequency") +
  myTheme

# Arrange the plots side by side
combined_plot_mtddm<- plot_grid(tasteweight1, tasteweight2, drift1, drift2, nDT1, nDT2, bound1, bound2, rst1, rst2, labels = c("a", "", "b", "", "c", "", "d", "", "e", ""), label_size = 20, ncol = 4, align = "h", column_spacing = unit(c(1, 3, 1, 1, 3, 1, 1, 3, 1), "cm"))
combined_plot_mtddm
# Save the combined plot as a PNG file
ggsave("combined_plot_mtddm_nutri.png", combined_plot_mtddm, width = 16, height = 12)

```